Toxic code snippets on Stack Overflow

### 2017-10-16 cloverflow-tse/cloverflow.tex

\textbf{EX: External Sources.} We found 199 clone pairs with evidence of cloning
from external sources to Stack Overflow. After getting rid of duplicated SO
snippets due to multiple intra-clone instances in Qualitas, we obtained 111 EX
pairs. Fifty pairs provide evidences of copying to both Stack
Overflow and Qualitas while the rest (61) provides evidence of copying to
Stack Overflow only. All of them contain statements giving an external source of the
cloned code which fall into six groups as displayed in \Cref{fig:ex_sources}. 
We discovered that 63 EX online clone pairs are copied from source code of classes or 
methods in Java SDK, 18 pairs are from websites, 15 pairs are from open source systems,
11 pairs are from Java official documentations from Sun Microsystems or Oracle,
3 pairs are from books, and 1 pair is from a company project.
For example, Stack Overflow Post
9549009 contains a code comment saying \textit{``Copied shamelessly from
	org.bouncycastle.crypto.generators.PKCS5S2ParametersGenerator''} which is an
open source project. Post 92962 includes a {\small\texttt{VerticalLabelUI}}
class with a license statement showing that it is developed by a private company
called \textsf{Sapient}. Post 12879764 has a text saying \textit{``Code modified
	and cleaned from the original at Filthy Rich Clients.''} which is a book for
developing animated and graphical effects for desktop Java applications. Another
example is a copy of code from a website in post 15260207. The text surrounding
source code reads ``\textit{I basically stole this from the web and modified it
	slightly... You can see the original post here
	(\url{http://www.java2s.com/Code/Java/Swing-JFC/DragListDemo.htm}).}''.
Interestingly, the code is actually a copy from Sun Microsystems.

>>>>

\textbf{EX: External Sources.} We found 199 clone pairs from external sources to
Stack Overflow. After consolidating duplicated SO snippets due to multiple
intra-clone instances in Qualitas, we obtained 111 EX pairs. We found evidence
of copying from an external source to Stack Overflow, but not in Qualitas, in 61 pairs. 
A stronger evidence of copying from an external source to both Stack
Overflow and Qualitas is available in the other 50 pairs. Each of them contains
statement(s) pointing to the original external location of the cloned code. Our
analysis shows that the external sources fall into six groups as displayed in
\Cref{fig:ex_sources}. There are 63 EX online clone pairs copied
from source code of Java SDK, 18 pairs from websites, 15 pairs from open
source systems, 11 pairs from Java official documentations from Sun
Microsystems or Oracle, 3 pairs from books, and 1 pair from a company
project. For example, Stack Overflow Post 9549009 contains a code comment saying
\textit{``Copied shamelessly from
	org.bouncycastle.crypto.generators.PKCS5S2ParametersGenerator''} which is an
open source project. Post 92962 includes a {\small\texttt{VerticalLabelUI}}
class with a license statement showing that it is developed by a private company
called \textsf{Sapient}. Post 12879764 has a text saying \textit{``Code modified
	and cleaned from the original at Filthy Rich Clients.''} which is a book for
developing animated and graphical effects for desktop Java applications. Another
example is a copy of code from a website in post 15260207. The text surrounding
source code reads ``\textit{I basically stole this from the web and modified it
	slightly... You can see the original post here
	(\url{http://www.java2s.com/Code/Java/Swing-JFC/DragListDemo.htm}).}''.
Interestingly, the code is actually a copy from Sun Microsystems.
